Trends in Mortality: Analyzing the Distribution of Death Licenses in Great Toronto Area in the Past Decade

### 2024-09-24 starter_folder-main/paper/paper.qmd
in progress

```
## Data trend {#sec-datachar}

@@

@@

>>>>

```
## Data trend {#sec-datachar} 
Generally speaking,

@@

# 首先，计算每个地区的年平均值
yearly_data <- data |>
  group_by(year, place_of_death) |>
  summarise(total_death_licenses = sum(death_licenses, na.rm = TRUE), .groups = 'drop')

# 计算总体的死亡许可证均值
overall_mean <- mean(yearly_data$total_death_licenses)

# 创建柱状图并添加均值线
ggplot(yearly_data, aes(x = as.factor(year), y = total_death_licenses, fill = place_of_death)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +  # Bar plot with dodge to show side by side
  geom_hline(yintercept = overall_mean, linetype = "dashed", color = "blue", size = 1) +  # 添加均值线
  theme_minimal() +
  labs(
    x = "Year", 
    y = "Total Death Licenses", 
    fill = "Place of Death",
    title = "Death Licenses per Year in Toronto and Outside City Limits",
    caption = "Data source: Your Dataset"
  ) +
  scale_fill_brewer(palette = "Set1") +  # Set color palette for places
  theme(legend.position = "bottom")

@@

overall_mean <- mean(data$death_licenses, na.rm = TRUE)

# 绘制每年的死亡许可证变化，并区分 Toronto 和 Outside City Limits
ggplot(data, aes(x = year, y = death_licenses, color = place_of_death)) +
  geom_line(stat = "summary", fun = mean, size = 1) +  # 绘制趋势线（每年平均）
  geom_hline(yintercept = overall_mean, linetype = "dashed", color = "blue") +  # 添加全局均值线
  theme_minimal() +
  labs(
    x = "Year",
    y = "Death Licenses",
    color = "Place of Death",
    title = "Death License Trends in Toronto and Outside City Limits",
    caption = "Data source: Opendatatoronto"
  ) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
